Rising from the Ashes II: A Hidden Abundance Bimodality in Illustris TNG

### 2024-09-07 paper/ms.tex

\subsection{Observations}\label{ssec:obs}
We make use of two observational data sets. First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}. We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4. These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's. This results in a sample of 54,777 stars. We use Fe to track total metallicity and Mg alone as an $\alpha$-element \red{TODO: add any additional details}.

@@

In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SoI, respectively. For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors. These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:errors} for plots of the observational errors). The error in \MgFe{} is not signficant, but the age error, which is $1\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line. The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.

@@

% \input{src/app.tex}
\end{document}

>>>>

\subsection{Observations}\label{ssec:obs}
We make use of two observational data sets. First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}. We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4. These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's. This results in a sample of 54,777 stars. We use Fe to track total metallicity and Mg alone as an $\alpha$-element.

@@

In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SoI, respectively. For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors. These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:obs_err} for plots of the observational errors). The error in \MgFe{} is not signficant, but the age error, which is $1\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line. The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.

@@

\appendix

\section{Observational Errors}\label{app:obs_err}
In Figure~\ref{fig:alpha}, we assumed observational errors of $15\%$ in age and $0.01\,\dex$ in \MgFe{}. In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC2 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively). We show our $15\%$ age error and $0.01\,\dex$ abundance error assumptions as black lines. For the age error, we used the maximum of the upper and lower estimates from \citet{2018ApJS..239...32P}. Our assumed errors are generally consistent with the errors. Our error in \MgFe{} is a bit smaller than in ASPCAP, but the age estimates are by far the more constraining of the two.

\begin{figure*}
  \centering
  \includegraphics[width=\columnwidth]{fig/obs_error.pdf}
  \caption{The observational errors of the APOKASC2 (left) and ASPCAP dataset (right). We show, on the left, a line indicating a $15\%$ error in observed age and on the right a vertical line indicating a $0.01\,\dex$ error.}
  \label{fig:obs_err}
\end{figure*}

\end{document}
